---
title: "Data_appendix"
author: "Lauren Meyer"
date: "3/28/2019"
output: pdf_document
---
Loading Data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mosaic)
library(readr)
library(ipumsr)
#ipumsdata <- read_csv("usa_00004.csv", locale = locale(encoding = "latin1"))
ddi <- read_ipums_ddi("usa_00004.xml")
ipumsdata <- read_ipums_micro(ddi)
#head(ipumsdata)
#save(ipumsdata, file = "ipumsdata.rda")
#ipumsdata <- read_csv("usa_00004.dat")
small_data <- ipumsdata %>%
  select(YEAR,SERIAL,STATEFIP,METRO,OWNERSHP,HHINCOME,PHONE,CINETHH,SEX,AGE,RACE,EDUC,EMPSTAT,OCC,INCTOT,FTOTINC,DIFFEYE,TRANTIME)
```

Structure and Names
```{r}
str(small_data)
```
There are 18 variables in the data, and 3,190,040 observations.
Variables: 
* YEAR: The year of the observation.
```{r}
favstats(~YEAR, data = small_data)
```
This dataset contains only the 2017 survey data. 

* SERIAL: Unique serial number assigned to each household.
```{r}
favstats(~SERIAL, data = small_data)
```
Expected distribution of a unique sequential code.

* STATEFIP: Numerical code signifying state. 
```{r}
favstats(~STATEFIP, data = small_data)
```
Max of 56 seems odd for a country with 50 states, but I'm guessing those are territory markers such as DC and Guam. 

* METRO: Is the household in a metropolitan area or not?
```{r}
favstats(~METRO, data = small_data)
```
This one seems to be a set of numerical codes, not an actual integer value. I'll have to convert this one to a factor variable before doing anything else with it.

* OWNERSHP: Code for whether and how the household owns their dwelling.
```{r}
favstats(~OWNERSHP, data = small_data)
```
This one is also an integer code, with levels 0, 1, and 2. Will need to convert to factor.

* HHINCOME: Total household income.
```{r}
favstats(~HHINCOME, data = small_data)
```
I'm curious how a household manages to get a negative household income. Maybe it factors in debts and other things?

* PHONE: Availability of a telephone.
```{r}
favstats(~PHONE, data = small_data)
```
Another factor variable. 

* CINETHH: Whether any member of the household has internet access.
```{r}
favstats(~CINETHH, data = small_data)
```
A lot of these seem to be factor variables.

* SEX: Binary int, male vs female.
```{r}
favstats(~SEX, data = small_data)
```
As expected, factors numbered 1 and 2. 

* AGE: Age of the respondent.
```{r}
favstats(~AGE, data = small_data)
```
Youngest is 0, oldest is 96. Seems accurate.

* RACE: Numerical code for race of respondent.
```{r}
favstats(~RACE, data = small_data)
```
Seems to be another factor variable. 

* EDUC: Highest year of schooling/educational attainment.
```{r}
favstats(~EDUC, data = small_data)
```
This survey really likes integer codes.

* EMPSTAT: Employment status. 
```{r}
favstats(~EMPSTAT, data = small_data)
```
This survey *really* likes integer codes.

* OCC: Occupation of worker.
```{r}
favstats(~OCC, data = small_data)
```
This one also seems coded, but there are a lot more codes than the rest of them.

* INCTOT: Personal income. 
```{r}
favstats(~INCTOT, data = small_data)
```
Again, negative income? Unsure how that factors in. 

* FTOTINC: Total family income.
```{r}
favstats(~FTOTINC, data = small_data)
```
I'm not sure where this negative income is coming from. At least the numbers otherwise make sense!

* DIFFEYE: Any vision disability, blindness, etc.
```{r}
favstats(~DIFFEYE, data = small_data)
```
This one seems simple, a basic binary code. 

* TRANTIME: Length of commute. 
```{r}
favstats(~TRANTIME, data = small_data)
```
I pity the person who has an 160-minute commute to work, but the rest of it looks good. 

Most Pressing, to do:
Convert the integer codes to factor levels, possibly rename the factor levels. 
Decide which variables we want to work with so we don't waste time fixing data we don't end up using.

```{r}
newdata<-small_data %>%
mutate(internet=if_else(CINETHH==3,0,
                if_else(CINETHH %in% 1:2,1,NA_real_)))
m1<-glm(internet ~ AGE, data = newdata)
m1
ggplot(data = newdata, aes(x = AGE, y = internet)) +
geom_point() 
qplot(x=as.factor(internet),y=AGE,data=newdata,geom="boxplot")+coord_flip()
ggplot(data = newdata, aes(x = as.factor(AGE), y = internet)) +
geom_bar(stat="identity")
```
```{r}
qplot(x=as.factor(internet),y=HHINCOME,data=newdata,geom="boxplot")+coord_flip()

```

```{r}
newdata %>%
group_by(as.factor(RACE)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(RACE)`)) + geom_bar(stat="identity")

qplot(x=as.factor(internet),y=AGE,data=newdata,geom="boxplot")+coord_flip()
ggplot(data = newdata, aes(x = as.factor(AGE), y = internet)) +
geom_bar(stat="identity")

```
```{r}
newdata %>%
group_by(as.factor(PHONE)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(PHONE)`)) + geom_bar(stat="identity")
```
```{r}
qplot(x=as.factor(internet),y=INCTOT,data=newdata,geom="boxplot")+coord_flip()
```
```{r}
qplot(x=as.factor(internet),y=TRANTIME,data=newdata,geom="boxplot")+coord_flip()
```

```{r}
newdata %>%
group_by(as.factor(PHONE)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(PHONE)`)) + geom_bar(stat="identity")
```


```{r}
newdata %>%
group_by(as.factor(SEX)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(SEX)`)) + geom_bar(stat="identity")

```
```{r}
newdata %>%
group_by(as.factor(EMPSTAT)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(EMPSTAT)`)) + geom_bar(stat="identity")

```
```{r}
newdata %>%
group_by(as.factor(DIFFEYE)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(DIFFEYE)`)) + geom_bar(stat="identity")

```

Surprising how no education is so high.
```{r}
newdata %>%
group_by(as.factor(METRO)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(METRO)`)) + geom_bar(stat="identity")
```

```{r}
newdata %>%
group_by(as.factor(OWNERSHP)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(OWNERSHP)`)) + geom_bar(stat="identity")

```
```{r}
newdata %>%
group_by(as.factor(STATEFIP)) %>%
 summarize(mean=mean(internet, na.rm=TRUE)) %>%
ggplot(aes(y=mean,x=`as.factor(STATEFIP)`)) + geom_bar(stat="identity")

```
